Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-01-21 paper.tex
Minor Query R12: Fig7a - perturbations vs profiles

\begin{figure}
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{perturbations_4.pdf}
      \caption{Perturbations}
      \label{fig:pressure_pert_4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{resonant_surface_4.pdf}
      \caption{Resonance function}
      \label{fig:resonant_surface_4}
    \end{subfigure}
\mycaption{Perturbations corresponding to the flute and kink instabilities and
the spatial radial distribution of the associated resonance
function.}{\rev{Gas pressure}
and velocity perturbations in $z$ (corresponding to the flute and kink
instabilities, respectively) and of the resonance surface $m B_{\theta}(r)/r
+ kB_z(r)$ as a function of $r$ using the observed fluting perturbation
wavenumbers. All plots are  snapshots at $t=26$ where $\eta=10^{-4}$ and the
viscosity model is anisotropic.} 
\label{fig:k_and_resonance}%
\end{figure}

The observed perturbations corresponding to the flute and kink instabilities at
$t=26$ are shown in Figure~\ref{fig:pressure_pert_4}. The fluting perturbation
is most easily observed in the pressure and is plotted as a function of $z$
following a line through the point $(r, \theta) = (0.101, 0)$. The kink
instability is best revealed in the $x$-velocity (a proxy for the radial
velocity) through the axis. Comparing the magnitudes of the perturbations at
this time suggests the flute instability is close to transitioning to its
nonlinear phase while the kink instability is still very much in its linear
phase.

>>>>

\begin{figure}
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{perturbations_4.pdf}
      \caption{\rev{Selected flow and pressure profiles.}}
      \label{fig:pressure_pert_4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{resonant_surface_4.pdf}
      \caption{Resonance function.}
      \label{fig:resonant_surface_4}
    \end{subfigure}
  \mycaption{\rev{\newold{Selected flow and pressure profiles and the 
resonance function defined by equation
\eqref{eq:resonant_surface}.}{Perturbations corresponding to the flute
        and kink instabilities and the spatial radial distribution of the associated resonance
function.}}}{\rev{(a) Gas pressure} and velocity \rev{profiles in $z$}
    \rev{at the fixed point $(r, \theta) = (0.101, 0)$} \rev{assuming the form of the most
      unstable modes}. (b) The resonance surface $m B_{\theta}(r)/r
+ kB_z(r)$ as a function of $r$ using the observed fluting perturbation
wavenumbers. All plots are  snapshots at $t=26$ where $\eta=10^{-4}$ and the
viscosity model is anisotropic.} 
\label{fig:k_and_resonance}%
\end{figure}

The \rev{flow and pressure profiles in the axial direction $z$} at
$t=26$ are shown in Figure~\ref{fig:pressure_pert_4} \rev{and at this
moment they assume the form of a superposition of the unstable modes
with the largest amplitude. In particular, the} fluting perturbation
  is most easily observed in the pressure \rev{profile and} \rev{\newold{}{ plotted
  as a function of $z$ following a line through the point $(r, \theta) = (0.101, 0)$.}} \rev{the} kink
instability is best revealed in the $x$-velocity (a proxy for the radial
velocity) through the axis. Comparing the magnitudes of the \rev{profiles} at
this time suggests the flute instability is close to transitioning to its
nonlinear phase while the kink instability is still very much in its linear
phase.
